Investigating the impact of interventionist causal approach on the study of verbal aggression and discrimination online

### 2021-09-08 paperDraft/paperDraft.Rmd

---
title: "Nesta attacks study"
author: "Patrycja Tempska and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    includes:
      in_header: Rafal_latex6.sty
  html_document:
    df_print: paged
  word_document: default
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/attacks.bib
csl: ../references/apa-6th-edition.csl
---

@@

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
2+2 #use this formatting for chunks
```
\normalsize

@@

Normative interventions can refer either to general social norms of civility and respect, community standards, a particular subreddit rule, or a descriptive norm among others.
E.g. Insulting others is against Reddit's policy. 
Hey there, we do not call each other like that here.
Empathetic interventions can refer to the emotional state of the recipient or the sender of the attack or both. They are designed to evoke an empathetic response. 
E.g. There is a human being on the other side who might be hurt by your words.
I see you are frustrated but remember the human.

>>>>

---
title: "Investigating the impact of interventionist causal approach on the study of verbal aggression and discrimination online"
author: "Patrycja Tempska and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    includes:
      in_header: Rafal_latex6.sty
  html_document:
    df_print: paged
  word_document: default
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/attacks.bib
csl: ../references/apa-6th-edition.csl
---

@@

\vspace{1mm}
\footnotesize

\normalsize

@@

\textbf{Empathetic interventions}
In the first treatment condition, volunteers were encouraged to send empathy-inducing messages focusing either on the target of verbal aggression (e.g. „Hey such words might hurt the other person”), stressing the common humanity aspect that we call share („We are all humans of flesh and blood”), or even infusing the intervention with the emphatic response to the attacker (Hey I understand your strong emotions…”). 
At the core of the empathetic interventions, we put forth the notion that goes back to David Hume and Adam Smith. The first one conceived empathy (at the time referred to as sympathy) as mirroring the emotional state of another person. In the academic psychological literature, similar phenomenon was distinguished and coined in the term emotional contagion
(https://www.sciencedirect.com/topics/psychology/emotional-contagion): "the process in which an observed behavioral change in one individual leads to the reflexive production of the same behavior by other individuals in close proximity, with the likely outcome of converging emotionally". For Adam Smith, sympathy consisted of visualizing how the sympathetic person would feel in the particular circumstances of the other --- thus here the process was based not so much on mirroring, but rather projecting my imagination of what it is like to be that person in a certain moment). Without further delving into the differentiation between those two, sympathy in both accounts is crucial in the constitution of human beings as social and moral creatures (https://plato.stanford.edu/entries/empathy/). It enables the emotional connection to others and concern for their well-being. 
In the psychological literature, various kinds of empathetic responses were distinguished - the aforementioned emotional contagion, affective/proper empathy, sympathy, personal distress or cognitive empathy ((https://plato.stanford.edu/entries/empathy/). During the experiment, we couldn’t observe or measure whether the empathetic response indeed was evoked. Also, interventions that stated that "such words might hurt the other person" have the underlying assumption that the receiver of the attack might be hurt, but in reality that might not even be the case. Intuitively, and following the argumentation of Thomas Nagel in “What is it like to be a bat?” one can only imagine what it is like - but for me - to be a bat or to be a receiver of the attack. To each observed or imagined experience there is an array of subjective quality to actually experiencing it and in this way receiving a particular message might be met with a unique reception by each conscious being. Also, full epistemic access to the mind and body of another is impossible. But even though such access is impossible and putting aside the broad spectrum of phenomena related to empathetic response, our goal was by utilizing interventions referring to empathy in various forms, changing the behavior of the attacker - convincing him to refrain from using verbal aggression towards others. Whether the message indeed gave rise to empathy was not of importance - one can imagine a hypothetical scenario of a successful intervention in which the attacker changed his behavior long-term and stopped attacking others, hopefully as a result of interventions, but the  empathetic response was not even evoked. The behavioral change could be induced by other motivations - e.g. unwillingness from the exclusion from the community. Thus the goal is not to evoke empathy, but through empathetic interventions - substantially limiting the use of verbal aggression.

\textbf{Normative interventions}
Normative interventions were grounded in broadly defined norms and normative theories expressed via various means - either specific community guidelines imposed by Reddit or through ethics - deontology, virtue ethics. Whatever the strategy was used, it was supposed to express the unacceptability of verbal aggression in a direct or non-direct way.

A more direct approach referred to deontology in which „actions are good or bad according to a clear set of rules” (https://ethics.org.au/ethics-explainer-deontology/). Such interventions could state that „we have a duty to respect each other during the discussions", „we have a moral obligation to act in a civil manner while participating in online communities”, „we shouldn’t use ad personam in here”. The basic assumption behind those interventions is that there is something we ought to do or are morally required to do - and such actions are the right actions. There are also actions we ought not to do - and such actions are morally wrongful. This line of thinking can be traced back to Immanuel Kant who thought that all universal moral obligations can stem from categorical imperative: “act only in accordance with that maxim through which you can at the same time will that it become a universal law” (Groundwork of the Metaphysic of Morals).

Yet other interventions were encouraged to be expressed in the light of virtue ethics and stressed the importance of adhering to or practicing certain virtues. Such a message was assumed to motivate the moral agent in the process of positive reinforcement and create a feeling of the desirability of certain behaviors, e.g. „capacity to be respectful in a heated discussion is a virtue and requires hard work”. The core assumption here is that the virtue itself is not genetically inherited but is rather a potential or a disposition of a character that can be practice and mastered like a practical skill (even though as mentioned by Natasza Szutta in [cite her book about virtue ethics] virtues and practical skills share some fundamental differences). NS distinguished two types of virtues - affective and cognitive. Affective virtues encompass the emotions and feelings that play an important and positive role in morality and can act as a support in the course of becoming a virtuous man. A cognitive virtue relates to the intellectual aspect in which one knows how to act in certain situations and understands the rules of morally rightful actions (e.g. what is kindness and how a kind man acts). Here, just as in the case of empathetic interventions, any attempts to measure whether the target of the intervention in the case of a positive outcome (behavioral change) indeed acted in a virtuous way. A virtue of kindness may manifest itself in particular behaviors but as such cannot be identified with the virtuous deed, as highlighted by Natasza Szutta. Although again, the goal of the experiment itself was to change the behavior of the attackers, and measuring whether particular messages contributed to more flourishing individuals in terms of virtue development and character creation lies beyond the scope of this work. Interventions could affect people either way - stimulate their moral reflections or limit their attacks due to consequentialist way of thinking and fear of potential outcomes (e.g. being excluded from the community).

Additionally, Reddit created their social etiquette called "Rediquette" (https://www.reddithelp.com/hc/en-us/articles/205926439) which is "an informal expression of the values of many redditors, as written by redditors themselves." All users are encouraged to abide by it and moderators of communities (called subreddits) existing as a part of the platform have the authority to exclude its members based either on the basis of breaking the rules of the reddiquette or any other local rules imposed by specific subreddit. Volunteers were encouraged to refer to those norms as well, citing specific points, for instance, "Hey there, have you read the reddiquette? It says remember the human". or "Let's recall the reddiquette and adhere to the same standards of behavior online that you follow in real life".

As we have seen, those two categories of interventions - normative and empathetic - encompass a whole variety of categories within. One might think that it would be useful to construct a more diverse set of treatment conditions in which we test each of the ethics or empathy differentiation separately - e.g. one for virtue ethics, deontology, perhaps utilitarian approach, empathy toward the receiver of the attack, empathy towards the attacker, so on and so forth. Additionally, different types of interventions could be tested and tailored depending on the spectrum on which one can be found in the foundations of moral reasoning, as proposed by Jonathan Haidt: Care/Harm, Fairness/Cheating, Loyalty/Betrayal, Authority/Subversion, Sanctity/Degradation, and Liberty/Oppression (J. Haidt, The Righteous Mind). Albeit for the sake of the sanity of our volunteers, we decided to create only two but broad categories and let them decide based on the context of the conversation, how they want to respond to the attacker.

### 2021-09-08 paperDraft/paperDraft.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames,enabledeprecatedfontcommands]{scrartcl}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Nesta attacks study},
  pdfauthor={Patrycja Tempska and Rafal Urbaniak},
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
%\documentclass{article}

@@

\title{Nesta attacks study}
\author{Patrycja Tempska and Rafal Urbaniak}
\date{}

@@

\begin{Shaded}
\begin{Highlighting}[]
\DecValTok{2}\SpecialCharTok{+}\DecValTok{2} \CommentTok{\#use this formatting for chunks}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 4
\end{verbatim}

@@

Normative interventions can refer either to general social norms of
civility and respect, community standards, a particular subreddit rule,
or a descriptive norm among others. E.g. Insulting others is against
Reddit's policy. Hey there, we do not call each other like that here.
Empathetic interventions can refer to the emotional state of the
recipient or the sender of the attack or both. They are designed to
evoke an empathetic response. E.g. There is a human being on the other
side who might be hurt by your words. I see you are frustrated but
remember the human.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames,enabledeprecatedfontcommands]{scrartcl}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Investigating the impact of interventionist causal approach on the study of verbal aggression and discrimination online},
  pdfauthor={Patrycja Tempska and Rafal Urbaniak},
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
%\documentclass{article}

@@

\title{Investigating the impact of interventionist causal approach on
the study of verbal aggression and discrimination online}
\author{Patrycja Tempska and Rafal Urbaniak}
\date{}

@@

@@

\textbf{Empathetic interventions} In the first treatment condition,
volunteers were encouraged to send empathy-inducing messages focusing
either on the target of verbal aggression (e.g.~„Hey such words might
hurt the other person''), stressing the common humanity aspect that we
call share („We are all humans of flesh and blood''), or even infusing
the intervention with the emphatic response to the attacker (Hey I
understand your strong emotions\ldots''). At the core of the empathetic
interventions, we put forth the notion that goes back to David Hume and
Adam Smith. The first one conceived empathy (at the time referred to as
sympathy) as mirroring the emotional state of another person. In the
academic psychological literature, similar phenomenon was distinguished
and coined in the term emotional contagion
(\url{https://www.sciencedirect.com/topics/psychology/emotional-contagion}):
``the process in which an observed behavioral change in one individual
leads to the reflexive production of the same behavior by other
individuals in close proximity, with the likely outcome of converging
emotionally.'' For Adam Smith, sympathy consisted of visualizing how the
sympathetic person would feel in the particular circumstances of the
other --- thus here the process was based not so much on mirroring, but
rather projecting my imagination of what it is like to be that person in
a certain moment). Without further delving into the differentiation
between those two, sympathy in both accounts is crucial in the
constitution of human beings as social and moral creatures
(\url{https://plato.stanford.edu/entries/empathy/}). It enables the
emotional connection to others and concern for their well-being. In the
psychological literature, various kinds of empathetic responses were
distinguished - the aforementioned emotional contagion, affective/proper
empathy, sympathy, personal distress or cognitive empathy
((\url{https://plato.stanford.edu/entries/empathy/}). During the
experiment, we couldn't observe or measure whether the empathetic
response indeed was evoked. Also, interventions that stated that ``such
words might hurt the other person'' have the underlying assumption that
the receiver of the attack might be hurt, but in reality that might not
even be the case. Intuitively, and following the argumentation of Thomas
Nagel in ``What is it like to be a bat?'' one can only imagine what it
is like - but for me - to be a bat or to be a receiver of the attack. To
each observed or imagined experience there is an array of subjective
quality to actually experiencing it and in this way receiving a
particular message might be met with a unique reception by each
conscious being. Also, full epistemic access to the mind and body of
another is impossible. But even though such access is impossible and
putting aside the broad spectrum of phenomena related to empathetic
response, our goal was by utilizing interventions referring to empathy
in various forms, changing the behavior of the attacker - convincing him
to refrain from using verbal aggression towards others. Whether the
message indeed gave rise to empathy was not of importance - one can
imagine a hypothetical scenario of a successful intervention in which
the attacker changed his behavior long-term and stopped attacking
others, hopefully as a result of interventions, but the empathetic
response was not even evoked. The behavioral change could be induced by
other motivations - e.g.~unwillingness from the exclusion from the
community. Thus the goal is not to evoke empathy, but through empathetic
interventions - substantially limiting the use of verbal aggression.

\textbf{Normative interventions} Normative interventions were grounded
in broadly defined norms and normative theories expressed via various
means - either specific community guidelines imposed by Reddit or
through ethics - deontology, virtue ethics. Whatever the strategy was
used, it was supposed to express the unacceptability of verbal
aggression in a direct or non-direct way.

A more direct approach referred to deontology in which „actions are good
or bad according to a clear set of rules''
(\url{https://ethics.org.au/ethics-explainer-deontology/}). Such
interventions could state that „we have a duty to respect each other
during the discussions``, „we have a moral obligation to act in a civil
manner while participating in online communities,'' „we shouldn't use ad
personam in here''. The basic assumption behind those interventions is
that there is something we ought to do or are morally required to do -
and such actions are the right actions. There are also actions we ought
not to do - and such actions are morally wrongful. This line of thinking
can be traced back to Immanuel Kant who thought that all universal moral
obligations can stem from categorical imperative: ``act only in
accordance with that maxim through which you can at the same time will
that it become a universal law'' (Groundwork of the Metaphysic of
Morals).

Yet other interventions were encouraged to be expressed in the light of
virtue ethics and stressed the importance of adhering to or practicing
certain virtues. Such a message was assumed to motivate the moral agent
in the process of positive reinforcement and create a feeling of the
desirability of certain behaviors, e.g.~„capacity to be respectful in a
heated discussion is a virtue and requires hard work''. The core
assumption here is that the virtue itself is not genetically inherited
but is rather a potential or a disposition of a character that can be
practice and mastered like a practical skill (even though as mentioned
by Natasza Szutta in {[}cite her book about virtue ethics{]} virtues and
practical skills share some fundamental differences). NS distinguished
two types of virtues - affective and cognitive. Affective virtues
encompass the emotions and feelings that play an important and positive
role in morality and can act as a support in the course of becoming a
virtuous man. A cognitive virtue relates to the intellectual aspect in
which one knows how to act in certain situations and understands the
rules of morally rightful actions (e.g.~what is kindness and how a kind
man acts). Here, just as in the case of empathetic interventions, any
attempts to measure whether the target of the intervention in the case
of a positive outcome (behavioral change) indeed acted in a virtuous
way. A virtue of kindness may manifest itself in particular behaviors
but as such cannot be identified with the virtuous deed, as highlighted
by Natasza Szutta. Although again, the goal of the experiment itself was
to change the behavior of the attackers, and measuring whether
particular messages contributed to more flourishing individuals in terms
of virtue development and character creation lies beyond the scope of
this work. Interventions could affect people either way - stimulate
their moral reflections or limit their attacks due to consequentialist
way of thinking and fear of potential outcomes (e.g.~being excluded from
the community).

Additionally, Reddit created their social etiquette called
``Rediquette''
(\url{https://www.reddithelp.com/hc/en-us/articles/205926439}) which is
``an informal expression of the values of many redditors, as written by
redditors themselves.'' All users are encouraged to abide by it and
moderators of communities (called subreddits) existing as a part of the
platform have the authority to exclude its members based either on the
basis of breaking the rules of the reddiquette or any other local rules
imposed by specific subreddit. Volunteers were encouraged to refer to
those norms as well, citing specific points, for instance, ``Hey there,
have you read the reddiquette? It says remember the human.'' or ``Let's
recall the reddiquette and adhere to the same standards of behavior
online that you follow in real life.''

As we have seen, those two categories of interventions - normative and
empathetic - encompass a whole variety of categories within. One might
think that it would be useful to construct a more diverse set of
treatment conditions in which we test each of the ethics or empathy
differentiation separately - e.g.~one for virtue ethics, deontology,
perhaps utilitarian approach, empathy toward the receiver of the attack,
empathy towards the attacker, so on and so forth. Additionally,
different types of interventions could be tested and tailored depending
on the spectrum on which one can be found in the foundations of moral
reasoning, as proposed by Jonathan Haidt: Care/Harm, Fairness/Cheating,
Loyalty/Betrayal, Authority/Subversion, Sanctity/Degradation, and
Liberty/Oppression (J. Haidt, The Righteous Mind). Albeit for the sake
of the sanity of our volunteers, we decided to create only two but broad
categories and let them decide based on the context of the conversation,
how they want to respond to the attacker.
